\Russell's Metatheoretic Study - Notes

### 2006-07-16 papers/ICFP'06-wmm/notes.tex
Got everything right without axioms, need to think about how to get elim of trans to Russell
Abandon idea of getting transitivity to other systems for now, concentrate on getting Russell in good shape

Then we have two versions of the \Russell type system.
The \coqmodule{Lambda.JRussell} directory contains a definition of
Russell with judgemental equality and a coercion relation with
transitivity and symetry built-in. It is the most declarative, and thus
the clearest presentation of \Russell, however we can't prove Subject
Reduction for this system directly. We proved basic metatheory for this
system up to validity.

The modules in \coqmodule{Lambda.Russell} define a more algorithmical
version of the \Russell type system. This version uses and untyped
conversion relation and an already refined coercion algorithm (without
transitivity).

>>>>

Then we have two versions of the \Russell type system.
The \coqmodule{Lambda.JRussell} directory contains a definition of
Russell with judgemental equality and a coercion relation with
transitivity and symetry built-in. It is the most declarative, and thus
the clearest presentation of \Russell, however we can't prove Subject
Reduction for this system directly. We proved basic metatheory for this
system up to validity and unicity of sorting, which we can transpose to
\TPOSR easily.

The modules in \coqmodule{Lambda.Russell} define a more algorithmical
version of the \Russell type system. This version uses an untyped
conversion relation and an already refined coercion algorithm (without
transitivity).

Finally, one can find in \coqmodule{Lambda.Meta} modules the
metatheorems about those systems, or more precisely the equivalence proofs.
